---
title: "Statistical Computation and Simulation"
author: '<span class="author-name"> Wei Li</span> 
<a href="https://wli169.expressions.syr.edu/">
  <svg width="15" height="15" viewBox="0 0 24 24" fill="none" xmlns="http://www.w3.org/2000/svg">
    <path d="M12 2L2 12H5V22H19V12H22L12 2Z" fill="black"/>
  </svg>
</a> 
<a href="https://github.com/weili-code">
  <svg width="15" height="15" viewBox="0 0 24 24" fill="none" xmlns="http://www.w3.org/2000/svg">
    <path d="M12 2C6.48 2 2 6.48 2 12C2 16.41 4.87 20.17 8.84 21.4C9.34 21.53 9.68 21.27 9.7 21C9.7 20.76 9.7 20.29 9.7 19.03C6.73 19.74 5.61 17.37 5.61 17.37C5.08 15.78 4.1 15.39 4.1 15.39C2.84 14.61 4.63 14.63 4.63 14.63C6.27 14.78 7.16 16.23 7.16 16.23C8.21 18.04 10.17 17.46 11 17.18C11.12 16.51 11.5 16.13 11.93 15.88C8.33 15.57 5.04 14.24 5.04 10.63C5.04 9.58 5.42 8.78 6 8.13C5.87 7.88 5.6 6.84 6.18 5.32C6.18 5.32 7.1 4.93 9.7 6.68C10.9 6.42 12.17 6.32 13.4 6.32C14.62 6.32 15.9 6.42 17.1 6.68C19.7 4.93 20.6 5.32 20.6 5.32C21.2 6.84 20.9 7.88 20.8 8.13C21.4 8.78 21.8 9.58 21.8 10.63C21.8 14.24 18.5 15.57 14.9 15.88C15.5 16.27 16 17.01 16 18.11C16 19.76 16 21 16 21.38C16 21.65 16.3 21.91 16.8 21.78C20.77 20.56 23.64 16.8 23.64 12C23.64 6.48 19.52 2 12 2Z" fill="black"/>
  </svg>
</a>
<a href="mailto:wli169@syr.edu">
  <svg width="15" height="15" viewBox="0 0 24 24" fill="none" xmlns="http://www.w3.org/2000/svg">
    <path d="M20 4H4C2.9 4 2 4.9 2 6V18C2 19.1 2.9 20 4 20H20C21.1 20 22 19.1 22 18V6C22 4.9 21.1 4 20 4ZM20 6V7.76L12 13L4 7.76V6H20ZM4 18V9.24L12 14.4L20 9.24V18H4Z" fill="black"/>
  </svg>
</a>'
date: "`r Sys.Date()`"
geometry: left=2cm, right=2cm, top=2cm, bottom=2cm
linestretch: 1.3
output:
  html_document:
        toc: no
        df_print: paged
        css: "https://cdnjs.cloudflare.com/ajax/libs/font-awesome/5.15.1/css/all.min.css"   
        mathjax_config:
          - TeX-AMS-MML_HTMLorMML             
  pdf_document: 
      keep_tex: yes  
      include:
        in_header: preamble_rmd.tex
fontsize: 14pt
header-includes:
- \usepackage{amsmath}
- \usepackage{bbm}
- \usepackage[linewidth=1pt]{mdframed}
- \newcommand\inner[2]{\left\langle#1,#2\right\rangle}
- \newcommand\floor[1]{\lfloor#1\rfloor}
- \newcommand\ceil[1]{\lceil#1\rceil}
- \newcommand\mb[1]{\mathbf{#1}}
- \newcommand\bs[1]{\boldsymbol{#1}}
- \newcommand\mr[1]{\mathrm{#1}}
- \newcommand\wh[1]{\widehat{#1}}
- \newcommand\op[1]{\operatorname{#1}}
- \newcommand\mbb[1]{\mathbb{#1}}
- \newcommand\E{\mathrm{E}}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \newcommand{\weic}[1]{\textcolor{red}{\text{(Wei:#1)}}}  
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({
    jax: ["input/TeX", "output/CommonHTML"],
    extensions: ["tex2jax.js"],
    TeX: {
      extensions: ["AMSmath.js", "AMSsymbols.js", "noErrors.js", "noUndefined.js"]
    },
    "HTML-CSS": {
      availableFonts: [],
      preferredFont: null,
      webFont: "TeX",
      imageFont: null
    },
    CommonHTML: {
      linebreaks: { automatic: true }
    },
    showMathMenu: false  // Disable the MathJax context menu
  });
</script>



<style>
.author-name {
    margin-right: 20px; /* Adjust this value as needed */
}
</style>

<!---- 
HTML produced by this script needs to be placed 
inside ./docs/ to be loaded on the Github server.
------>

<!------------->

```{r include=FALSE}
# Load necessary libraries
library(ggplot2)

# Use the mtcars dataset
data(mtcars)

# Fit a linear model predicting mpg based on weight
fit <- lm(mpg ~ wt, data=mtcars)

# Summary of the fit
summary(fit)

# Plot the data and add the regression line
ggplot(mtcars, aes(x=wt, y=mpg)) +
  geom_point() +
  geom_smooth(method="lm", color="blue")

```


```{r echo=FALSE, results='hide'}
library(reticulate)
myenvs=conda_list()
print(myenvs)
#use_python("/Users/wli169/miniconda3/bin/python", required = T) # base conda env
use_condaenv("py38torch_arm", required = TRUE)
reticulate::py_config()

```

```{python echo=FALSE, results='hide'}
import torch
print("PyTorch is working!" if torch.cuda.is_available() else "PyTorch is loaded, but CUDA is not available.")
```

```{python echo=FALSE, results='hide'}
print(torch.tensor([1, 2, 3]))
```

```{python include=FALSE}
# Import the required libraries
import numpy as np
import matplotlib.pyplot as plt

# Generate 100 random normal values for x and y
x = np.random.randn(100)
y = np.random.randn(100)

# Create a scatter plot using matplotlib
plt.scatter(x, y)

# Add title and labels
plt.title('Random Scatter Plot')
plt.xlabel('Random X Values')
plt.ylabel('Random Y Values')

# Display the plot
plt.show()
```


```{r include=FALSE}
#rmarkdown::render("./Lecture/1_basics.Rmd", quiet = TRUE)
#rmarkdown::render("./Lecture/2_Solving_Linear_Systems.Rmd", quiet = TRUE)
```

<!-- ```{r child = "2.Rmd"} -->
<!-- ``` -->

<!-- ```{r child = "3.Rmd"} -->
<!-- ``` -->

<!------------->


## Preface

Outline of materials for the topics in Statistical Computation and Simulation (in progress). Feel free to contact me if you find any typo or error.

## Topics

- [Review: basics](1_basics.html)
- [Solving linear systems](2_Solving_Linear_Systems.html)
- [Eigen-decomposition, SVD](3_Eigen_SVD.html)
- [Principal components](4_Principal_Component.html)
- [Basics of optimization](5_basics_of_optimization.html)
- [Gradient descent](6_gradient_descent_newton.html)
- [Modern optimization](7_modern_optimization.html)
- [Random variable generation](8_random-variable_generation.html)
- [Monte Carlo Integration](9_Monte_Carlo_Integration.html)
- [EM Algorithm](10_EM_algorithm.html)
- [Simulated Annealing](11_Simulated_Annealing_Others.html)
- [Basic Metropolis](12_Basics_MC_Metropolis.html)
- [MCMC](13_MCMC.html)
- [MCMC2](14_MCMC2.html)
- [RJMCMC](15_RJMCMC.html)
- [HMC](16_HMC.html)



#### License 

Shield: [![CC BY-NC-SA 4.0][cc-by-nc-sa-shield]][cc-by-nc-sa]

This work is licensed under a
[Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License][cc-by-nc-sa].

[![CC BY-NC-SA 4.0][cc-by-nc-sa-image]][cc-by-nc-sa]

[cc-by-nc-sa]: http://creativecommons.org/licenses/by-nc-sa/4.0/
[cc-by-nc-sa-image]: https://licensebuttons.net/l/by-nc-sa/4.0/88x31.png
[cc-by-nc-sa-shield]: https://img.shields.io/badge/License-CC%20BY--NC--SA%204.0-lightgrey.svg